A pipeline to analyse time-course gene expression data

### 2020-06-05 scripts/manuscript.Rmd
possible fix for caption data

```{r echo=FALSE, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE, autodep=TRUE, warning=FALSE, error=FALSE, message=FALSE,
  echo=TRUE,
  duplicate.label="allow"
)
```

@@

knitr::include_graphics("images/fig1_schemas.png")

@@

```{r echo=FALSE, fig.width=6, fig.height=3, fig.caption="Distribution of variance"}
hist(variance_per_genes, breaks=100, col="black", xlab="Variance",
     ylab="# probes", main="")
abline(v=min_variance, col="#AB0000", lw=2)
```

@@

```{r  correlation_plot, fig.width=6, fig.height=6, fig.caption="Cross-correlation of the samples"}
# Reorder the conditions such that:
#	- Control is before any influenza treatment
#	- Each treatment is ordered from low to high pathogeny
meta$Group = factor(meta$Group, levels(meta$Group)[c(3, 2, 1, 5, 4)])

@@

```{r echo=FALSE, fig.width=3, fig.height=3, fig.caption="Distribution of DE genes per condition"}
num_de = colSums(qvalues < 0.05)
names(num_de) = c(
    "Kawasaki", "California", "Vietnam LD", "Vietname HD")
barplot(num_de, col="black", ylab="Number of DE genes")
```

@@

```{r echo=FALSE, fig.height=6, fig.width=6, fig.caption="Confusion matrix between the two sets of labels"}
genes_scored = names(labels)

>>>>

```{r echo=FALSE, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE, autodep=TRUE, warning=FALSE, error=FALSE, message=FALSE,
  echo=TRUE, fig.width=4,
  duplicate.label="allow",out.extra = "")

@@

knitr::include_graphics("images/fig1_schemas.png",dpi=30 )

@@

```{r echo=FALSE, fig.width=6, fig.height=3, fig.cap="Distribution of variance"}
hist(variance_per_genes, breaks=100, col="black", xlab="Variance",
     ylab="# probes", main="")
abline(v=min_variance, col="#AB0000", lw=2)
```

**EAP**: Not sure why you hide the code for this plot, but not for others...

@@

```{r  correlation_plot, fig.width=6, fig.height=6, fig.cap="Cross-correlation of the samples"}
# Reorder the conditions such that:
#	- Control is before any influenza treatment
#	- Each treatment is ordered from low to high pathogeny
meta$Group = factor(meta$Group, levels(meta$Group)[c(3, 2, 1, 5, 4)])

@@

```{r echo=FALSE, fig.width=3, fig.height=3, fig.cap="Distribution of DE genes per condition"}
num_de = colSums(qvalues < 0.05)
names(num_de) = c(
    "Kawasaki", "California", "Vietnam LD", "Vietname HD")
barplot(num_de, col="black", ylab="Number of DE genes")
```

@@

```{r echo=FALSE, fig.height=6, fig.width=6, fig.cap="Confusion matrix between the two sets of labels"}
genes_scored = names(labels)
